### 2023-01-03 writeups/Observations.tex
fix model evaluation

Three machine learning models were used: SVMs, Decision Trees, and Naïve Bayes classifiers. Each of those models was used for Boolean and type classification and with three seperate text representations (Bag-of-Words, raw frequency, and TF-IDF), making a total of 18 models. For the sake of evaluation, the rules-based model was retrained on only the training data, then tested on the test data. Models labeled RB are rules-based. The scores represent the proportion of the test dataset that the model correctly predicted, 1 means perfect predictions, 0 means entirely incorrect predictions. The models were evaluated using 10-fold cross-validation. Tables with rankings for the specific algorithms and text representations are given after.

@@

\begin{center}
Table 4: Algorithm comparison --- binary classification\\
\begin{tabular}{ |c|c| }
\hline {\bf Model type}& {\bf Score}\\
\hline Support Vector Machine & 0.714\\
\hline Decision Tree & 0.568\\
\hline Naïve Bayes & 0.466\\
\hline
\end{tabular}
\end{center}

\begin{center}
Table 5: Representation comparison --- binary classification\\
\begin{tabular}{ |c|c| }
\hline {\bf Representation}& {\bf Score}\\
\hline TF-IDF & 0.550\\
\hline Frequency & 0.516\\
\hline Bag of Words & 0.507\\
\hline
\end{tabular}
\end{center}

Using a Friedman Chi Squared test, the p-value for table 3 is $6.30 \times 10^{-89}$, the p-value for the different algorithms is $4.39 \times 10^{-73}$, and the p-value for the different representations is $5.21 \times 10^{-10}$.

@@

\begin{center}
Table 7: Algorithm comparison --- type classification\\
\begin{tabular}{ |c|c| }
\hline {\bf Model type}& {\bf Score}\\
\hline Support Vector Machine & 0.479\\
\hline Decision Tree & 0.321\\
\hline Naïve Bayes & 0.300\\
\hline
\end{tabular}
\end{center}

\begin{center}
Table 8: Representation comparison --- type classification\\
\begin{tabular}{ |c|c| }
\hline {\bf Representation}& {\bf Score}\\
\hline TF-IDF & 0.397\\
\hline Bag of Words & 0.347\\
\hline Frequency & 0.338\\
\hline
\end{tabular}
\end{center}

>>>>

Three machine learning models were used: SVMs, Decision Trees, and Naïve Bayes classifiers. Each of those models was used for Boolean and type classification and with three seperate text representations (Bag-of-Words, raw frequency, and TF-IDF), making a total of 18 models. For the sake of evaluation, the rules-based model was retrained on only the training data, then tested on the test data. Models labeled RB are rules-based. The scores represent the proportion of the test dataset that the model correctly predicted, 1 means perfect predictions, 0 means entirely incorrect predictions. The models were evaluated using 10-fold cross-validation. Tables with rankings for the specific algorithms and text representations are given after, these were taken by getting the accuracy scores of the most common responses given by the models that use that representation or algorithm.

@@

\begin{center}
Table 4: Algorithm comparison --- binary classification\\
\begin{tabular}{ |c|c| }
\hline {\bf Model type}& {\bf Score}\\
\hline Decision Tree & 0.767\\
\hline Support Vector Machine & 0.754\\
\hline Naïve Bayes & 0.600\\
\hline
\end{tabular}
\end{center}

\begin{center}
Table 5: Representation comparison --- binary classification\\
\begin{tabular}{ |c|c| }
\hline {\bf Representation}& {\bf Score}\\
\hline Bag of Words & 0.766\\
\hline Frequency & 0.761\\
\hline TF-IDF & 0.749\\
\hline
\end{tabular}
\end{center}

Using a Friedman Chi Squared test, the \emph{p}-value for table 3 is $6.30 \times 10^{-89}$, the \emph{p}-value for the different algorithms is $1.98 \times 10^{-59}$, and the \emph{p}-value for the different representations is $1.18 \times 10^{-16}$.

@@

\begin{center}
Table 7: Algorithm comparison --- type classification\\
\begin{tabular}{ |c|c| }
\hline {\bf Model type}& {\bf Score}\\
\hline Decision Tree & 0.582\\
\hline Naïve Bayes & 0.535\\
\hline Support Vector Machine & 0.524\\
\hline
\end{tabular}
\end{center}

\begin{center}
Table 8: Representation comparison --- type classification\\
\begin{tabular}{ |c|c| }
\hline {\bf Representation}& {\bf Score}\\
\hline Frequency & 0.588\\
\hline Bag of Words & 0.585\\
\hline TF-IDF & 0.541\\
\hline
\end{tabular}
\end{center}

Using a Friedman Chi Squared test, the \emph{p}-value for table 6 is $2.52 \times 10^{-29}$, the \emph{p}-value for the different algorithms is $1.00 \times 10^{-11}$, and the \emph{p}-value for the different representations is $0.0014$.
